TEMPERATURES AND METALLICITIES FOR 10,000+ M DWARFS IN THE \apogee\ SURVEY

### 2018-08-11 paper/draft.tex
add boyajian ref

\newcommand{\apogee}{\textsl{APOGEE}}
\newcommand{\thecannon}{\textsl{The Cannon}}
\newcommand{\cannon}{\textsl{Cannon}}
\newcommand{\aspcap}{\textsl{ASPCAP}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\zmass}{\textsl{2MASS}}
\newcommand{\sdssiv}{\textsl{SDSS-IV}}
\newcommand{\teff}{$T_{\rm eff}$}

@@

The spectral type sample consists of 51 sources, spanning M0-M9 cross-matched from the \citealt{West:2011} (hereafter W11) catalog of 78,841 M dwarfs from SDSS. For each source in the catalog, spectral types were determined both through an automated routine using The Hammer \citep{Covey:2007} and by visual inspection to a reported accuracy of $\pm$1 type.

>>>>

\newcommand{\apogee}{\textsl{APOGEE}}
\newcommand{\thecannon}{\textsl{The Cannon}}
\newcommand{\cannon}{\textsl{Cannon}}
\newcommand{\aspcap}{\textsl{ASPCAP}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\zmass}{\textsl{2MASS}}
\newcommand{\sdss}{\textsl{SDSS}}
\newcommand{\sdssiv}{\textsl{SDSS-IV}}
\newcommand{\teff}{$T_{\rm eff}$}

@@

The spectral type sample consists of 51 sources, spanning M0-M9 cross-matched from the \citealt{West:2011} (hereafter W11) catalog of 78,841 M dwarfs from \sdss. For each source in the catalog, spectral types were determined both through an automated routine using The Hammer \citep{Covey:2007} and by visual inspection to a reported accuracy of $\pm$1 type.
